The 4th Workshop on Sustainable Software: Best Practices and Experiences (WSSSPE4)

### 2016-06-10 WSSSPE4_proposal/WSSSPE4_proposal.tex
updates

\item {\bf Other Personnel: } No funds requested.
\item {\bf Fringe Benefits: }  No funds requested. 
\item {\bf Equipment: }  No funds requested. 
\item {\bf Travel: } \$3,000

{\it National travel for the US based organizers to attend the workshop in New Orleans. Funds will be used to contribute towards airfares and/or the two hotel nights needed for the workshop}

\item {\bf Participant Support: } \$20,000
{\it Funds are requested to support travel for 18 participants and 2 presenters from US institutions across the country to travel to New Orleans. Estimated costs include airfare, 2 nights hotel and workshop fees.}

@@

As for WSSSPE1, all material (including publications, presentations, meeting minutes, real time discussions) will be open, hosted and archived on existing public platforms (e.g. Slideshare, ArXiv, Google Docs, Twitter). The WSSSPE web page and wiki will be additionally used.

>>>>

\item {\bf Other Personnel: } No funds requested.
\item {\bf Fringe Benefits: }  No funds requested. 
\item {\bf Equipment: }  No funds requested. 
\item {\bf Travel: } \$6,000

{\it International travel for the U Illinois based organizers to attend the meeting in Manchester, UK. Funds will be used to contribute towards airfares and/or the hotel nights needed for the workshop}

\item {\bf Participant Support: } \$40,000
{\it Funds are requested to support travel for 18 participants and 2 presenters from US institutions across the country to travel to New Orleans. Estimated costs include airfare, 2 nights hotel and workshop fees.}

@@

As for previous WSSSPE meetings, all material (including publications, presentations, meeting minutes, real time discussions) will be open, hosted and archived on existing public platforms and journals (e.g. Slideshare, ArXiv, Google Docs, Twitter). The WSSSPE web page and wiki will be additionally used.
